---
title: "SAND Output Report"
date: "`r paste('Report Date: ', toOrdinal::toOrdinalDate(Sys.Date()))`"
author: "`r paste('Licensed to:', params$licensed_user)`"
always_allow_html: true
output: 
    pdf_document:
      df_print: default
      toc: yes
    word_document:
      df_print: default
      toc: yes
      toc_depth: '4'
    html_document:
      toc: true
      toc_depth: 3
      toc_float: true
      self_contained: yes
      mode: selfcontained
      theme: journal
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[C]{SAND Report}
  - \fancyfoot[C]{CONFIDENTIAL REPORT}
  - \fancyfoot[L]{\thepage}
  - \usepackage{comment}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{makecell}
params:
  report_format: NA
  plots: NA
  tables: NA
  text_interpretation: NA
  introductory_text: NA
  sand_inputs: NA
  validity_text: NA
  output_name: NA
  dates: NA
  demographics_inputs: NA
  licensed_user: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = F)
library(knitr)
library(kableExtra)
library(tinytex)
library(flextable)
# Global options
knitr::opts_chunk$set(echo = FALSE, ft.tabcolsep=0, ft.latex.float = "none")
flextable::set_flextable_defaults(fonts_ignore=TRUE) # or get warnings

# Printing options depending on report format
if(params$report_format == 'html'){
  options(knitr.table.format = 'html')
  } else if (params$report_format == 'pdf') {
    options(knitr.table.format = 'latex')
  } else {
    options(knitr.table.format = 'markdown')
  }
```

`r if(params$report_format != "docx") {"\\begin{comment}"}`

# SAND Scoring Report

`r if(params$report_format != "docx") {"\\end{comment}"}`

`r colorize("PAPER RECORD FORM REQUIRED WITH EACH ADMINISTRATION TO ACCOMPANY THIS REPORT", "red")`

## Background Information

```{r background_table, results='asis'}
## Splits data by defined number of columns
  split_df_into_columns <- function(df, column_number){
    df %>% 
      split.default(., ceiling(seq_along(df)/column_number))
  }

# Add age, split into four column rows, print each row as separate table
  params$demographics_inputs %>%
    mutate(age = params$dates$age, .before = 5) %>% 
    split_df_into_columns(., column_number = 4) %>%
    purrr::set_names(c("Examinee", "Testing", "Background", "Additional Information")) %>%
    imap(., ~{
        table_print(.x, caption = .y, output_format = params$report_format, size = 10)
     }) -> out 
          if(params$report_format == 'html'){
            map(out, ~cat(knitr::knit_print(.x), "\n"))
            # invisible(cat(knitr::knit_print(table_print(out, output_format = params$report_format, size = 6))))
          }-> suppress_print_msg else{
                 map(out, ~cat(knitr::knit_print(.x %>% 
                                                align(., i = 1, j = NULL, align = "left", part = "header")), "\n"))
            } -> suppress_print_msg
```

## Introduction

`r if(params$report_format == "pdf") {"\\begin{comment}"}`

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = 'blue'>

`r params$introductory_text`

</div>
`r if(params$report_format == "pdf") {"\\end{comment}"}`

`r if(params$report_format != "pdf") {"\\begin{comment}"}`

`r params$introductory_text`

`r if(params$report_format != "pdf") {"\\end{comment}"}`

## Validity

```{r individual_print, results='asis'}

# Subchunkify will add a separate chunk within a chunk. Useful if need to change options, like height, width
subchunkify <- function(g, fig_height=7, fig_width=5) {
  g_deparsed <- paste0(deparse(
    function() {g}
  ), collapse = '')

  sub_chunk <- paste0("
  `","``{r sub_chunk_", floor(runif(1) * 10000), ", fig.height=",
   fig_height, ", fig.width=", fig_width, ", echo=FALSE}",
  "\n(", 
    g_deparsed
    , ")()",
  "\n`","``
  ")

  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}

## HTML output
  if(params$report_format == "html"){
  ## Validity plot, table, text output
    subchunkify(params$plots[[1]], fig_height = 5, fig_width = 6)
    invisible(cat(knitr::knit_print(table_print(params$tables[[1]], output_format = params$report_format, size = 10))))
    invisible(cat(params$validity_text, '\n'))

## Scales plot, table, text output
    cat('\n\n', "## Scales", '\n\n')
  lapply(1:4, function(i) {
    cat(paste("<h4>", params$output_name[-1][i], "</h4></hr>"))
    cat("<div class = 'row h-100'>")
      subchunkify(params$plots[-1][[i]], fig_height = 3, fig_width = 10)
    cat("</div>")
    cat("<div class = 'row h-100'>")
      cat("<div class = 'col-md-6'>")
        invisible(cat(knitr::knit_print(table_print(params$tables[-1][[i]], output_format = params$report_format, size = 10))))
      cat("</div>")
      cat("<div class = 'col-md-6'>")
        invisible(cat(params$text_interpretation[[i]]))
      cat("</div>")
    cat("</div>")
  }) -> suppress_print_msg

###*** Code if pdf or word
  } else {
  ## Validity plot, table, text output
    subchunkify(params$plots[[1]], fig_height = 3, fig_width = 6)
    invisible(cat(knitr::knit_print(table_print(params$tables[[1]], output_format = params$report_format, size = 10))))
    invisible(cat(params$validity_text))
    cat("\n")
    pander::pandoc.header("Scales", level = 2)
    cat('\n')
  ## Scales plot, table, text output
  lapply(1:4, function(i) {
  ###*** THis will print section headers. Reuse and replace level and title. Will not abstract to function
    cat("  \n###", params$output_name[-1][[i]], "  \n")
    subchunkify(params$plots[-1][[i]], fig_height = 5, fig_width = 10)
    cat("\n")
    invisible(cat(knitr::knit_print(table_print(params$tables[-1][[i]], output_format = params$report_format, size = 6))))
    invisible(cat(params$text_interpretation[[i]]))
    cat("\n")
  })-> suppress_print_msg
  }

```

## Endorsed Items

```{r endorsed_items_table,results = 'asis'}
# Endorsed df, grouped by form, scale, give first result as header section for those
tags$style('#myid * { word-wrap: break-word; color: blue }') 
  params$sand_inputs %>%
          group_by(questionnaire) %>% 
          mutate(
            questionnaire = case_when(
              questionnaire== "observation" ~ "Observation",
              TRUE ~ "Interview"
            ),
            Source = ifelse(duplicated(questionnaire), "", questionnaire),
            Modality = ifelse(duplicated(Modality), "", Modality),
            Subscale =ifelse(duplicated(Subscale), "", Subscale)
          ) %>% 
          ungroup() %>% 
          dplyr::select(Source, Modality, "  Subscale" = Subscale, Item = item, Response = input_value) -> out 
          if(params$report_format == 'html'){
            invisible(cat(knitr::knit_print(table_print(out, output_format = params$report_format, size = 6))))
          } else{
                 invisible(cat(knitr::knit_print(table_print(out, 
                                                             output_format = params$report_format, 
                                                             size = 4) %>%
                                                  fontsize(., size = 6, part = "body") %>% 
                                                  fontsize(., size = 4, j = 1)
                               )))
          }
```


<!-- insert logo -->
```{r, echo=FALSE, message=F, warning=F, fig.align="center", out.width= '50%', out.height= '50%'}
# Add logo to output
library(jpeg)
library(grid)
library(gridExtra)
url <- "https://stoeltingco.com/Psychological/media/stoelting_logo.jpg"
z <- tempfile()
download.file(url,z,mode="wb")
img <- readJPEG(z)
rimg <- rasterGrob(as.raster(img)) # raster multilayer object
tg <- textGrob("Stoelting Psychology", gp=gpar(fontfamily = "serif", fontsize = 20))
sg1 <- textGrob("www.stoeltingco.com", gp=gpar(fontfamily = "sans", fontsize = 10))
sg2 <- textGrob("620 Wheat Lane", gp=gpar(fontfamily = "sans", fontsize = 10))
sg3 <- textGrob("Wood Dale, IL, USA 60191", gp=gpar(fontfamily = "sans", fontsize = 10))
sg4 <- textGrob("psychtests@stoeltingco.com", gp=gpar(fontfamily = "sans", fontsize = 10))
sg5 <- textGrob("630-860-9700", gp=gpar(fontfamily = "sans", fontsize = 10))
lay <- rbind(c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,2),
             c(1,3),
             c(1,4),
             c(1,5),
             c(1,6),
             c(1,7),
             c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,NA))
grid.arrange(rimg, tg, sg1, sg2, sg3, sg4, sg5, layout_matrix = lay)
grid.rect(width = 1.5, height = .5, gp = gpar(lwd = 2, col = "blue", fill = NA))
```
&nbsp;

<!-- html contact links footer -->
```{r contact_info, echo=FALSE, results= 'asis'}
  cat("<p style=\"text-align: 
      center;\">Copyright 2022:<a href=\"https://www.stoeltingco.com\" target = \"_blank\">Stoelting</a></p>")
if (params$report_format == "html"){
  cat("<p style=\"text-align: center;\"><a style=\"color: #0645AD;\" href = \"mailto:psychtests@stoeltingco?subject = SAND App&body = Message\"><em>Email Stoelting for support</em></a></p>")
}
```

